Template settings for rmarkdown files (formatting, specific packages)

# YAML header

- geometry : sets margins of page
-  classoption: changes orientation to landscape
-  mainfont: indicates font for xelatex to produce
-  output: pdf_document - forces pdf output (default is html)
-  latex_engine: xelatex - helps with customized font sizes 
-  knit (function) - changes output directory of Test.pdf
---
geometry: margin=1cm
mainfont: Arial
classoption:
  - landscape
output: 
  pdf_document:
    latex_engine: xelatex
knit: (function(inputFile, encoding) {
      out_dir = 'foo/bar';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'Test.pdf'))})
---

# Setup block
- echo = F : hides code chunks in output (typically preferred for sharing with non-analysts)
- comment = NA : hides comments from R Console output

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(comment = NA)

# Sets output for qwraps tables to markdown and left align figures
options(qwraps2_markup = "markdown")
options(fig.align='left')

# Sets directory to root of folder instead of current folder
# This helps organize rmd files separately from parent folder
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

# Chunk options

```{r, results='asis'}
# Creates page break between two elements
cat("\n\n\\pagebreak\n")
```

# Latex inline options 

- \fontsize{25}{30}: indicates size and vertical spacing of font
- \fontseries{b}: bolds font
- \selectfont: applies changes
- \center: centers code chunk output
