Template settings for rmarkdown files (formatting, specific packages)

# PDF - YAML
- geometry : sets margins of page
-  classoption: changes orientation to landscape
-  mainfont: indicates font for xelatex to produce
-  output: pdf_document - forces pdf output (default is html)
-  latex_engine: xelatex - helps with customized font sizes 
-  knit (function) - changes output directory of Test.pdf
---
geometry: margin=1cm
mainfont: Arial
classoption:
  - landscape
output: 
  pdf_document:
    latex_engine: xelatex
knit: (function(inputFile, encoding) {
      out_dir = 'foo/bar';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'Test.pdf'))})
---

## PDF - Setup block
- echo = F : hides code chunks in output (typically preferred for sharing with non-analysts)
- comment = NA : hides comments from R Console output

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(comment = NA)

# Sets output for qwraps tables to markdown and left align figures
options(qwraps2_markup = "markdown")
options(fig.align='left')

# Sets directory to root of folder instead of current folder
# This helps organize rmd files separately from parent folder
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

## PDF - Chunk options

```{r, results='asis'}
# Creates page break between two elements
cat("\n\n\\pagebreak\n")
```

## PDF - Latex inline options 

- \fontsize{25}{30}: indicates size and vertical spacing of font
- \fontseries{b}: bolds font
- \selectfont: applies changes
- \center: centers code chunk output

## HTML - YAML
---
output:
  html_document: default
  word_document: default
---

## HTML - Setup
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

## HTML - reporting 

Sets directory path for manuscript file output

```{r}
dir_path = paste0('manuscript/figures/')
```

### Table 1 - tableby package

Requires tableby package and includes helper functions for additional summaries

```{r, results='asis'}
    
Format_PVal = function(val) {
  if (val < 0.001) {
    result = "< 0.001"
  } else {
    result = round(val, 3)
  }
  return(result)
}

swilk = function(x, weights = rep(1, length(x)), ...) {
  swilk_pval = shapiro.test(x)[['p.value']]   
  return(Format_PVal(swilk_pval))
  }

Count_NA = function(x, weights = rep(1, length(x)), ...) {
  missing = sum(is.na(x))
  total = length(x)
  
  missing_pct = round((missing / total) * 100, 2)
  
  if (missing != 0) {
    out_label = paste0(missing, ' (', missing_pct, '%)')
  } else {
    out_label = 'None'
  }
  return(out_label)
}

# Use to reorder vars by count
demo_df$Var = reorder(demo_df$Var, demo_df$Var, function(x) -length(x))

# Use to change how a var is displayed in the table
attr(demo_df$Var, 'label') = "Table label"

# All numeric vars will have the following info summarized
# Count_NA: N(%) missing values
stat_labels_tbl1 = list(Count_NA = 'Missing values', medianq1q3 = 'Median (Q1, Q3)', 
                  meansd = 'Mean (SD)', swilk = 'Shapiro-Wilk p-value')

# kwt - kruskal wallis; fe - fisher exact; chisq - chi square
table_1 = tableby(Facet_Var ~ kwt(Var1) + fe(Var2) + chisq(Var3), data = demo_df,
              test = TRUE, numeric.stats= c('meansd', 'medianq1q3', 'swilk', 'Count_NA'),
              stats.labels = stat_labels_tbl1, digits = 2)

# pfootnote automatically adds which tests were conducted as a footnote
out_1 = summary(table_1, pfootnote = TRUE)

# writes table to html output
out_1
```

Saves above table output to word doc

```{r, results='hide'}
write2word(out_1, paste0(dir_path, 'tables/Table1.doc'),
           title="Demographic and Clinical Features of Study Patients")
```


### Formatted dataframes (premade tables)

Requires huxtable package. Makes cells contaning '***' (sig p vals) bold

```{r, results = 'asis'}
as_huxtable(df) %>%
  add_colnames() %>%
  set_font_size(10) %>%
  map_bold(by_regex('[***]' = TRUE)) %>%
  theme_plain() %>%
  print_html()
```

### Figures

All figures should be saved to the workspace in the original source file.
This makes it easier for plots to be consistent between the source file and the .Rmd,
while also improving knitting speed.

Template knits the figure to html and saves a publication-ready figure to the 
manuscript folder (.tiff files are like 20 mb typically)

## Figure 1

```{r, fig.width=10, fig.height=10}
fig_1
ggsave(paste0(dir_path, "plots/Fig1"), device = "tiff", width = 10, height = 10)
```
